\chapter{Research \& Background Reading}
The body of literature surrounding electronic glosses is rich in varied. The research done for the sake of this project is structured in two parts.
\begin{enumerate}
	\item Whether or not electronic glosses are effective in developing the skills of reading comprehension and vocabulary retention.
	\item A look at which design aspects of electronic glosses are most effective in developing those skills.
	\item Background research into recommender systems (Not done at time of progress report) 
\end{enumerate}

\section{Effectiveness of Electronic Glosses}
First, it should be established whether or not an electronic gloss might be an effective for increasing vocabulary retention and reading comprehension. If not, then there is little to no reason in continuing in development of this project, as it will fail to be effective in its goals. 

\textcite{abraham2008} finds that, overall, that learners with access to an electronic gloss will perform better than learners without access, in both skills of reading comprehension and vocabulary retention, particularly on intermediate learners. They note that the small sample size of studies analysed should mean that their study is not seen as conclusive evidence, however suggestive evidence is enough to establish that development of this project should continue.

Another caveat that should also be added that most of the studies analysed in \textcite{abraham2008} are of tailor-made glosses designed for a specific text, as such the research findings of these studies and the meta-study may not be fully applicable to this project.


\section{Design Methods of Electronic Glosses}

Next it should be established the best way to design a gloss to most effectively increase the desired skill set in the learner. \textcite{roby1999} identifies three main parts of a gloss' design, its presentation, its taxonomy and its density. However, as density for this project's application is something determined by the leaner, background reading into design was limited to presentation and taxonomy. 

\subsection{Gloss Presentation}
\textcite{roby1999} defines gloss presentations is how the gloss is presented relative to the text, primarily this is about the location of the gloss content, however other factors such as colour schemes are also part of it.

\textcite{chen2016} identifies the three most researched gloss presentations as: in-text, marginal and pop up.  \textcite{abuseileek2008} finds that out of these three the marginal presentation category performs the best in both vocabulary retention and reading comprehension, while \textcite{marefat2016} finds that pop-ups are more effective than marginal for reading comprehension. As \textcite{chen2016} says, there has not been sufficient research into gloss location for valid conclusions to be drawn. 

\subsection{Gloss Taxonomy}
Gloss taxonomy is the content of the gloss. What is presented 

