\chapter{Project Description}
\section{Problem}

There have been a number of gloss tools developer for assisting a learner with L2 learning. Most of these tools are tailored to a text or set of texts and cannot be applied generally, this means that there is no guarantee that the learner will find the glossed texts interesting, leading to the learning not engaging with the text to the extent that they might if they enjoyed reading about the subject of the text. There may also be words not in the gloss that the learner does not know, and words in the gloss that the leaner already knows. 


A learner, especially an intermediate learner will struggle to perform the reading required on news site home pages and aggregate sites to find texts related to their interests. 
\section{Goals}

The goal of this project is to develop a program that will provide a custom gloss that can be applied to every article, only glossing text that the learner requests. The gloss will then display information related to the word that has been selected, this information can then be dismissed by the learner.

The program will also suggest articles to the learner based on the previously read articles and selected categories. 



\section{Scope}

The scope of this project is the building of a web application that fills the above goals. It will allow the leaner to select categories, and then recommend articles to them based on this selection. The user will then select an article and the article will then be presented to the user in a readable format.

Once on the article view, the leaner can then select a word by clicking on it, the application will then show a gloss with information about the selected word. Once it is no longer needed, this information can be dismissed. The learner will then be able return to the  article selection screen, to select another article and any words in the gloss at that time will preserved in the new article. 